Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
bleh

ROI mapping. ROI mapping is a form of feature selection, wherein only a subset of the d-dimensional input space is used. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features such as the standard deviation, kurtosis and skewness within ROIs did not increase predictability, these were not included in the subsequent analysis. ROIs require \textit{a priori} knowledge. When this knowledge is inaccurate, it results a inductive bias.

@@

So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

>>>>

ROI mapping. ROI mapping is a form of feature selection, wherein only a subset of the d-dimensional input space is used. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features such as the standard deviation, kurtosis and skewness within ROIs did not increase predictability, these were not included in the subsequent analysis. ROIs require \textit{a priori} knowledge. When this knowledge is inaccurate, it results in a inductive bias.

@@
